Add Plant Functional Type (PFT) labels

### 2021-03-30 R/add_plant_functional_type.Rmd
120 done

@@

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "???"       # ???
    taxon_pft_lookup$commonName[i] = "black cherry"}

>>>>

  else if(genusSpecies == "Pisonia albida"){
    taxon_pft_lookup$pft[i] = "???"    # Growth Form - Multiple Stem, Height, Mature - 30ft
    taxon_pft_lookup$commonName[i] = "corcho bobo"}

  else if(genusSpecies == "Platanus occidentalis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "American sycamore"}

  else if(genusSpecies == "Populus deltoides"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "eastern cottonwood"}

  else if(genusSpecies == "Populus grandidentata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "bigtooth aspen"}

  else if(genusSpecies == "Populus sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "cottonwood"}

  else if(genusSpecies == "Prosopis glandulosa"){
    taxon_pft_lookup$pft[i] = "???"   # shrub or tree ranging from 4 to 6m tall
    taxon_pft_lookup$commonName[i] = "honey mesquite"}

  else if(genusSpecies == "Prosopis velutina"){
    taxon_pft_lookup$pft[i] = "???" # deciduous shrub or tree is less than 15 m
    taxon_pft_lookup$commonName[i] = "velvet mesquite"}

  else if(genusSpecies == "Prunus americana"){
    taxon_pft_lookup$pft[i] = "???" # deciduous large shrub or small tree, reaching heights up to 15 feet
    taxon_pft_lookup$commonName[i] = "American plum"}

  else if(genusSpecies == "Prunus angustifolia"){
    taxon_pft_lookup$pft[i] = "woody_shrub" # short, thickly branched shrub 3 to 10ft tall
    taxon_pft_lookup$commonName[i] = "Chickasaw plum"}

  else if(genusSpecies == "Prunus mexicana"){
    taxon_pft_lookup$pft[i] = "???"
    taxon_pft_lookup$commonName[i] = "Mexican plum"}

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "???"       
    taxon_pft_lookup$commonName[i] = "black cherry"}

  else if(genusSpecies == "Quercus coccinea"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "scarlet oak"}

  else if(genusSpecies == "Quercus falcata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "southern red oak"}

  else if(genusSpecies == "Quercus geminata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sand live oak"}

  else if(genusSpecies == "Quercus hemisphaerica"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Darlington oak"}

  else if(genusSpecies == "Quercus laevis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "turkey oak"}

  else if(genusSpecies == "Quercus laurifolia"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "laurel oak"}

  else if(genusSpecies == "Quercus lyrata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "overcup oak"}

  else if(genusSpecies == "Quercus macrocarpa"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "bur oak"}

  else if(genusSpecies == "Quercus margaretta"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sand post oak"}

  else if(genusSpecies == "Quercus marilandica"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "blackjack oak"}

  else if(genusSpecies == "Quercus michauxii"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "swamp chestnut oak"}

  else if(genusSpecies == "Quercus montana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "chestnut oak"}

  else if(genusSpecies == "Quercus muehlenbergii"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "chinquapin oak"}

  else if(genusSpecies == "Quercus nigra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "water oak"}

  else if(genusSpecies == "Quercus pagoda"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "cherrybark oak"}

  else if(genusSpecies == "Quercus phellos"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "willow oak"}

  else if(genusSpecies == "Quercus rubra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "northern red oak"}

@@
